---
output: github_document
editor_options: 
  chunk_output_type: console
---


```{r, include = FALSE}
library( tidyverse )
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```


<!-- badges: start -->
<!-- badges: end -->



# poststratIV

Package to post-stratify an IV estimate to increase precision.  Also has replication code for associated paper, including code to run the simulations and generate synthetic RCT with non-compliance data.



## Demo of use

First we make or load some data:

```{r}
library( poststratIV )
dat = make_dat( N = 1000,
                params = default_sim_params() )
```

Then we estimate, declaring the outcome, compliance indicator, treatment assignment indicator, and stratification variable (baseline categorical variable of some sort):

```{r}
res <- IV.est.strat( dat, 
                     Yobs="Yobs", S="S", Z="Z", strat_var="X" )
res %>%
    dplyr::select( Xblk, ITT.hat, pi.hat, LATE.hat, SE.wald ) %>%
    knitr::kable( digits = 2 )
```

There is also the usual IV with no covariate adjustment:

```{r}
res <- IV.est( dat, 
                     Yobs="Yobs", S="S", Z="Z" )
knitr::kable( res, digits=2 )
```

